### 2021-12-14 input/proposal.tex
meow

Algorithm~\ref{algo:add} shows the few instructions that implement a
\emph{reactive} forwarding of best to reach consistent partitioning in
a static network where \processes never join, crash, nor leave the
system. As soon as a \process receives a better message, it delivers
and forwards it. The trade-off consists in decreasing termination time
at cost of increased traffic.  Figure~\ref{fig:add} illustrates the
behavior of this algorithm on a system comprising 4 \processes $a$,
$b$, $c$, and $d$. Both $a$ and $d$ become sources.  They \NAMEB
notifications $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
state with the lowest value $0$ (see Line~\ref{line:lowestbound}), and
send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, $b$ receives $\alpha_{d}^{1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. In Figure~\ref{fig:addD}, $b$ discards
$\alpha_{a}^{2}$, for it does not improve its partition
distance. Neither $c$ nor $d$ will ever acknowledge that Source~$a$
exists. Ultimately, \processes discard last transiting messages.
Despite the obvious lack of traffic optimization, the system reaches
consistent partitioning.

@@

As a cascading effect, in Figure~\ref{fig:problemD}, not only $c$
wrongfully believes that it belongs to $a$'s partition when $a$
already deleted it, but it could contribute to its inconsistency by
blocking farther but up-to-date messages from actual sources. To reach
consistent partitioning, \processes need
\begin{inparaenum}[(i)]
\item to detect possibly blocking conditions 
\item to purge all stale messages from the system
\item enabling up-to-date notifications to eventually echo back to
  every \process.
\end{inparaenum}
\TODO{A lot of blockings occur, only that of example is a problem.
  Could be $b$ or $c$ that detects? We put burden on $c$ since
  unconsistency starts here. Problem: how to make sure that $c$
  receives a staleness notification in this case?}

\begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
  \implies$ \underline{D}etector existence (D)] Assuming
  $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on $\pi_{xz}$ of
  $\alpha_x$ with $\alpha_x = \min D_z$, if $x$ broadcasts a staleness
  notification $\delta_x$, either $z$ eventually delivers it, or a
  \process $y$ in such a chain of delivery $\pi_{xz}'$ eventually
  \TODO{detects} its \TODO{blocking}.
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}

>>>>

Algorithm~\ref{algo:add} shows the few instructions that implement a
\emph{reactive} forwarding of best to reach consistent partitioning in
a static network where \processes never join, crash, nor leave the
system. As soon as a \process receives a better message, it delivers
and forwards it. The trade-off consists in decreasing termination time
at cost of increased traffic.  Figure~\ref{fig:add} illustrates the
behavior of this algorithm on a system comprising 4 \processes $a$,
$b$, $c$, and $d$. Both $a$ and $d$ become sources.  They \NAMEB
notifications $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
state with the lowest value $0$ (see Line~\ref{line:lowestbound}), and
send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, $b$ receives $\alpha_{d}^{1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. In Figure~\ref{fig:addD}, $b$ discards
$\alpha_{a}^{2}$, for it does not improve its partition
distance. Neither $c$ nor $d$ will ever acknowledge that Source~$a$
exists.  The protocol lacks of obvious traffic optimization, \eg grey
messages are useless in this scenario. Nevertheless, the system
discards last transiting messages after it reached consistent
partitioning.

@@

As a cascading effect in Figure~\ref{fig:problemD}, not only $c$
wrongfully believes that it belongs to $a$'s partition when $a$
already deleted it, but it could contribute to its inconsistency by
blocking farther but up-to-date messages from actual sources.

To reach consistent partitioning, \processes need
\begin{inparaenum}[(i)]
\item to detect possibly blocking conditions
\item to purge all stale messages from the system
\item enabling up-to-date notifications to eventually echo back to
  every \process.
\end{inparaenum}
Since Figure~\ref{fig:problemD} highlights that when the protocol
terminates, $c$ is the \process that remains in the wrong partition,
we put the burden of detection and resolution on it.

\TODO{A lot of blockings occur, only that of example is a problem.
  Could be $b$ or $c$ that detects? We put burden on $c$ since
  unconsistency starts here. Problem: how to make sure that $c$
  receives a staleness notification in this case? Also, $b$ is not
  sure to receive $\delta_c$ since composable problem.}

\begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
  \implies$ \underline{D}etector existence (D)] Assuming
  $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on $\pi_{xz}$ of
  $\alpha_x$ with $\alpha_x = \textup{last}~D_z$, if $x$ broadcasts a staleness
  notification $\delta_x$, either $z$ eventually delivers it, or a
  \process $y$ in such a chain of delivery $\pi_{xz}'$ eventually
  acknowledges its blocking.
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}
